---
title: "polarisR: Tips, Requirements, and Support"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{polarisR: Tips, Requirements, and Support}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE, 
  message = FALSE
)
```

This vignette provides supplementary information for using `polarisR`, including best practices, technical requirements, and support resources.

```{r setup}
library(polarisR)
```

## Tips and Best Practices

**Data Quality Considerations:**

*   Ensure sufficient numeric columns for analysis
*   Handle missing values before upload
*   Consider data scaling if variables have very different ranges
*   Minimum 50+ observations recommended for stable NLDR results

## Technical Requirements

*   **R Version**: R >= 4.1.0
*   **quollr Version**: 0.3.7
*   **Key Dependencies**: shiny, plotly, DT, quollr, Rtsne, umap
*   **Browser**: Modern web browser with JavaScript enabled
*   **Memory**: Sufficient RAM for your dataset size (recommend 4GB+ for large datasets)

## Support

For questions, bug reports, or feature requests, please visit:

*   **GitHub Repository**: https://github.com/Divendra2006/polarisR
*   **Issues**: https://github.com/Divendra2006/polarisR/issues
